### 2016-08-03 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to reports, updated West event times in propane gas burner report

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   127		  		&    116		\\
	~(3)~  1st floor west double door opened 	&	247		  		&    238 	 	\\
	~(4)~  1st floor east double door opened 	&   382			  	&    356		\\
	~(5)~  2nd floor east double door opened	&   517			  	&    484		\\
	~(6)~  PPV fan on 							&   587			  	&    596		\\
	~(7)~  PPV fan off              			&   731			  	&    746		\\
	~(8)~  All burners off 						&   757			  	&    776		\\
	~(9)~  2nd floor south exterior door opened &   836			  	&    836		\\
	(10) PPV fan on 	 						&   997			  	&    926		\\
	(11) 2nd floor south exterior door closed   &   1113		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   120		  		&    110		\\
	~(3)~ 1st floor west double door opened 	&	240		  		&    241 	 	\\
	~(4)~ 2nd floor west double door opened 	&   360			  	&    350		\\
	~(5)~ 2nd floor south exterior door opened	&   480			  	&    470		\\
	~(6)~ PPV fan on 							&   600			  	&    590 		\\
	~(7)~ All burners off 						&   720 		  	&    710		\\
	~(8)~ 2nd floor east double door opened 	&   855			  	&    830		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage

>>>>

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   195		  		&    133		\\
	~(3)~  1st floor west double door opened 	&	315		  		&    255 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    374		\\
	~(5)~  2nd floor east double door opened	&   586			  	&    501		\\
	~(6)~  PPV fan on 							&   653			  	&    614		\\
	~(7)~  PPV fan off              			&   800			  	&    764		\\
	~(8)~  All burners off 						&   830			  	&    797		\\
	~(9)~  2nd floor south exterior door opened &   899			  	&    850		\\
	(10) PPV fan on 	 						&   1066		  	&    943		\\
	(11) 2nd floor south exterior door closed   &   1179		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   120		  		&    114		\\
	~(3)~ 1st floor west double door opened 	&	240		  		&    245 	 	\\
	~(4)~ 2nd floor west double door opened 	&   360			  	&    354		\\
	~(5)~ 2nd floor south exterior door opened	&   480			  	&    474		\\
	~(6)~ PPV fan on 							&   600			  	&    595 		\\
	~(7)~ All burners off 						&   720 		  	&    715		\\
	~(8)~ 2nd floor east double door opened 	&   855			  	&    N/A		\\
	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 962		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage
